Manifold Destiny - or how to rig an election

### 2023-12-30 presentation.qmd
scriptokay

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
format:
  revealjs: 
    smaller: true
    toc-depth: 1
    toc: true 
webr: 
  show-startup-message: true    # Disable displaying status of webR initialization
  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
#source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
```

>>>>

---
title: "Manifold Destiny - or how to rig an election"
subtitle: "Based upon the ideas developed by Edward K. Solomon"
#format:
#  revealjs: 
#    smaller: true
#    toc-depth: 1
#    toc: true 
webr: 
  show-startup-message: true    # Disable displaying status of webR initialization
  packages: ['dplyr','purrr','magrittr','data.table','tidyr'] # Install R packages on document open
filters:
- webr 
footer: <https://lotariohw26.github.io/ManifoldDestiny/>
---

```{r, echo=F, message=F, warning=F}
library(ManifoldDestiny)
library(ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
library(RefManageR)
library(huxtable)
modlat <- eqpar$meql
md <- ManifoldDestinyWASMD::metad
source(paste0(rprojroot::find_rstudio_root_file(),'/script/simulations.R'))
source(paste0(rprojroot::find_rstudio_root_file(),'/script/applications.R'))
metad <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
mda <- jsonlite::fromJSON(paste0(rprojroot::find_rstudio_root_file(),"/data-raw/metadata.json"))
```
